Data Prep

### 2024-03-13 scripts/00.0_dataPrep.qmd
test gps jamming data for ryan

# tidy up
rm(ornitela)
rm(minDate)
rm(maxDate)
gc()
```

>>>>

# Also get some to test GPS jamming (for Ryan 2/28/24)
mindate_jamming <- "2023-10-01"
maxdate_jamming <- "2024-02-01"
test_jamming_ornitela <- vultureUtils::downloadVultures(loginObject = MB.LoginObject, removeDup = T, dfConvert = T, quiet = T, dateTimeStartUTC = mindate_jamming, dateTimeEndUTC = maxdate_jamming)
write_csv(test_jamming_ornitela, file = here("data/dataPrep/test_jamming_ornitela.csv"))

# tidy up
rm(ornitela)
rm(minDate)
rm(maxDate)
rm(mindate_jamming)
rm(maxdate_jamming)
rm(test_jamming_ornitela)
gc()
```
